%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{iftex}
\usepackage{fontspec}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{setspace}
\usepackage{tabularx}
\ifPDFTeX
  \input{glyphtounicode}
\fi
\usepackage{fontawesome5}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

\setmainfont[
  Path=fonts/,
  UprightFont=Geist-Regular.ttf,
  BoldFont=Geist-Bold.ttf,
  ItalicFont=Geist-Regular.ttf,
  BoldItalicFont=Geist-Bold.ttf,
  ItalicFeatures={FakeSlant=0.2},
  BoldItalicFeatures={FakeSlant=0.2}
]{Geist}
\setsansfont[
  Path=fonts/,
  UprightFont=Geist-Regular.ttf,
  BoldFont=Geist-Bold.ttf,
  ItalicFont=Geist-Regular.ttf,
  BoldItalicFont=Geist-Bold.ttf,
  ItalicFeatures={FakeSlant=0.2},
  BoldItalicFeatures={FakeSlant=0.2}
]{Geist}
\setmonofont[
  Path=fonts/,
  UprightFont=Geist-Regular.ttf
]{Geist}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\setlength{\footskip}{8pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\setstretch{1.08}

% Sections formatting
\titleformat{\section}{
  \vspace{-2pt}\bfseries\raggedright\small
}{}{0em}{}[\color{black}\titlerule \vspace{-2pt}]

% Ensure that generated PDFs remain machine readable when using pdfLaTeX.
\ifPDFTeX
  \pdfgentounicode=1
\fi

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \small #3 & \textit{\small #4} \\
    \end{tabular*}\vspace{-3pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small #1 & \textit{\small #2} \\
    \end{tabular*}\vspace{-3pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \footnotesize#1 & \footnotesize#2 \\
    \end{tabular*}\vspace{-3pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[itemsep=4pt, topsep=4pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeSkillRow}[2]{%
  \textbf{#1} & \footnotesize #2 \\
}
\newcommand{\resumeSkillSpacer}{%
  & \\
}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Jan Jiménez Serra} & \small {\faGlobe}\ \href{https://janjs.dev}{\underline{janjs.dev}} \\
\end{tabular*}
\vspace{2pt}

\noindent
{\footnotesize
  \faGithub\ \href{https://github.com/janjs}{\underline{github.com/janjs}}
  \hspace{0.5em} $|$ \hspace{0.5em}
  \faPhone\ +34 684 22 55 70
  \hspace{0.5em} $|$ \hspace{0.5em}
  \faEnvelope\ \href{mailto:jan.jime.serra@gmail.com}{\underline{jan.jime.serra@gmail.com}}
  \hspace{0.5em} $|$ \hspace{0.5em}
  \faMapMarker\ Netherlands (Originally from Barcelona)
}




%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {AI Software Engineer}{October 2021 -- Present}
      {Accenture Netherlands}{Amsterdam (Netherlands)}
      \resumeItem{Promoted twice while growing into AI-focused engineering roles spanning \textbf{LLM platforms}, \textbf{agentic systems}, and enterprise AI products.}

      \resumeItemListStart
      \resumeItem{German Industrial Machinery (2026 -- Present): Built \textbf{Next.js-based agentic systems} using \textbf{LLMs}, \textbf{RAG}, and enterprise integrations.}
      \resumeItem{US Medtech (2023 -- 2025): Built an internal \textbf{AI chatbot platform} used daily by \textbf{50,000+ employees}, using \textbf{Azure OpenAI} and \textbf{AWS Bedrock} with enterprise workflows, context-aware agents, and no-code tools for citizen developers.}
      \resumeItem{Large Dutch Bank (2021 -- 2023): Helped replace a 20+ year legacy user account platform with Kotlin, Spring, AngularJS, Azure SQL, and Cosmos DB, building backend services serving \textbf{1,000+ QPS} with \textbf{$>$99.9\% availability} and single-digit millisecond API latency.}
    \resumeItemListEnd
    
    \resumeSubheading
      {Full-stack Software Engineer}{April 2018 -- Dec. 2019}
      {NexoTech}{Mataró, Barcelona (Spain)}
      \resumeItemListStart
        \resumeItem{Led project about designing and building of a full-stack web application build in ReactJS and Java Spring for counting the amount of people in a building with IoT and Deep Learning implementations.}
        \resumeItem{Implemented a Machine Learning model with Keras and Python that recognizes gender and age. Used AWS Rekognition in production for better speed and accuracy.}
      \resumeItemListEnd

    \resumeSubHeadingListEnd


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {M.Sc. in Computer Science}{Sep. 2020 -- Oct. 2021}
      {Trinity College Dublin}{Dublin, Ireland}
      \resumeItemListStart
        \resumeItem{Specialized in \textbf{AR/VR}, \textbf{Machine Learning}, and \textbf{Computer Graphics}.}
      \resumeItemListEnd
    \resumeSubheading
      {Bachelor’s in Computer Engineering and Information Systems}{Sep. 2016 -- Dec. 2019}
      {Universitat Pompeu Fabra}{Barcelona, Spain}
      \resumeItemListStart
        \resumeItem{Studied a semester abroad at \textbf{Ajou University} in \textit{Suwon, South Korea}.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
      
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {Highlighted projects are listed below; more web, mobile, and open-source work can be found at: \href{https://github.com/janjs}{\underline{github.com/janjs}}.}{}
          \resumeItemListStart
            \resumeItem{\textbf{Chordwise} --- AI-powered chord progression generator for musicians, built with Next.js, OpenAI API, and Convex.}
            \resumeItem{\textbf{Scandrop MCP} --- MCP server that helps LLMs reason about and interact with 3D spatial environments, built with Python, TypeScript, and 3D processing pipelines.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \item \footnotesize{
      \begin{tabularx}{\linewidth}{@{}>{\raggedright\arraybackslash}p{0.2\linewidth}@{\hspace{0.45em}}X@{}}
        \resumeSkillRow{Languages}{\textbf{TypeScript/JavaScript} · \textbf{Python} · Java · Kotlin · Swift}
        \resumeSkillRow{Frameworks}{\textbf{Next.js} · \textbf{React} · \textbf{Node.js} · Spring · Angular · ThreeJS · React Native · iOS · ARKit/ARCore · Strudel}
        \resumeSkillRow{ML \& Spatial}{PyTorch · AWS Rekognition · Computer Vision · 3D Processing · Augmented Reality}
        \resumeSkillRow{Cloud, Data \& APIs}{\textbf{Azure} · SQL (PostgreSQL) · NoSQL (CosmosDB and MongoDB) · Mapping APIs · Enterprise Integrations}
        \resumeSkillRow{Developer Tools}{Git · Cursor · Claude Code · OpenAI Codex · VS Code · IntelliJ · Xcode · Azure DevOps · Convex}
        \resumeSkillRow{AI \& Agentic}{\textbf{AI Agents} · \textbf{RAG} · Model Context Protocol · Prompt Engineering · Azure AI Foundry · OpenAI API · AWS Bedrock · Hugging Face · Replicate · Roboflow}
        \resumeSkillSpacer
        \resumeSkillRow{Spoken Languages}{English (C1, Cambridge Advanced) · Spanish (Native) · Catalan (Native) · Dutch (Beginner)}
      \end{tabularx}
    }
 \end{itemize}


%-------------------------------------------
\end{document}
